Optimal (Multiway) Spatial Joins

### 2024-05-28 msj.tex
yufei

\noindent {\underline{\em Example 5.2.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_1, h_3, v_2)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_2)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \qed

>>>>

\noindent {\underline{\em Example 5.2.}} Segment $h_1$ has no left-covering rectangle in $R_2$ and thus has no trimmed segment. Segment $h_2$ has $\beta_2$ and $\beta_3$ as its left-covering rectangles. As the entire $h_2$ is covered by $\beta_2$
\qed
